Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-07-12 Manuscript/manuscript.Rmd
methods edits

Class imbalance was characterized by each dataset's *proportion of imbalance* (PI), [??? Why? It is bounded [0, 0.5], never seen it is used.] defined as the ratio of minority class observations to the sum of minority and majority class observations:

$$PI = \dfrac{C_{min}}{C_{min} + C_{maj}}$$

where $C_{min}$ denotes the complementary set of genomic bins that did overlap with a flanked TAD boundary and $C_{maj}$ denotes the set of genomic bins that did not overlap with a flanked TAD boundary. In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling). They are described in detail below.

>>>>

Class imbalance was characterized by each dataset's *proportion of imbalance* (PI) defined as the ratio of minority class observations to the sum of minority and majority class observations:

$$PI = 2\dfrac{C_{min}}{C_{min} + C_{maj}}$$

where $C_{min}$ denotes the set of genomic bins that overlap with a flanked TAD boundary and $C_{maj}$ denotes the complementary set of genomic bins that did not overlap with a flanked TAD boundary. Here, PI is bounded by 0 and 1, with heavily imbalanced classes approaching 0.

In order to assess the influence of imbalanced classes, we then evaluated four re-sampling techniques (in addition to no re-sampling). They are described in detail below.
